A modal logical multiverse for commutative algebra and combinatorics

### 2022-11-06 slides-paris2022.tex
Fixed timeline

{\usebackgroundtemplate{\begin{minipage}{\paperwidth}\vspace*{3.59cm}\includegraphics[width=\paperwidth]{staircase}\end{minipage}}
\begin{frame}{A brief timeline}
  \begin{itemize}
    \item[18xx] Cantor studies the \hil{continuum hypothesis}, the claim
    that~$2^{\aleph_0} = \aleph_1$.
    \item[19xx] Zermelo and Fraenkel offer the axioms of~\textsc{zfc}.
    \item[1938] Gödel proves: If~\textsc{zfc} is consistent, then so
    is~\textsc{zfc}+\textsc{ch}.
    \item[1963] Cohen proves: If~\textsc{zfc} is consistent, then so
    is~\textsc{zfc}+$\neg$\textsc{ch}.
    \item[since 1963 and ongoing] Set theorists pursue additional axioms to
    settle~\textsc{ch} (one way or another).  % XXX persue?
    \item[201x] Hamkins offers his paper on the \hil{multiverse position} in
    the philosophy of set theory, arguing that the program of pursing
    additional axioms (while successful in many ways) is doomed to fail in
    settling~\textsc{ch}.
  \end{itemize}
\end{frame}
\begin{frame}{The set-theoretic multiverse}
  \begin{tikzpicture}[remember picture,overlay]
    \node[xshift=-1.5cm,yshift=-3.5cm] at (current page.north east)
    {\includegraphics[width=2cm]{branching}};
  \end{tikzpicture}
  \vspace*{-1.5em}

>>>>

{\usebackgroundtemplate{\begin{minipage}{\paperwidth}\vspace*{3.59cm}\includegraphics[width=\paperwidth]{staircase}\end{minipage}}
% https://tex.stackexchange.com/a/198372/32372
\newcommand\ytl[2]{%
  \parbox[b]{4.5em}{\hfill{#1}~$\cdots\cdots$~}%
  \makebox[0pt][c]{\color{mypurple}$\bullet$}{\color{mypurple}\vrule}\quad%
  \parbox[c]{8.4cm}{\vspace{7pt}\raggedright#2\\[7pt]}%
  \\[-2.0pt]}
\begin{frame}{A brief timeline}
  \vspace*{-1.0em}
  \parbox[b]{4.5em}{\hfill\phantom{x}}\makebox[0pt][c]{\phantom{b}}{\color{mypurple}\vrule}\\[-3.5pt]
  \ytl{1878}{Cantor advances the \hil{continuum hypothesis}, the claim
  that~$2^{\aleph_0} = \aleph_1$.}
  \pause
  \ytl{1910s}{Zermelo--Fraenkel set theory emerges.}
  \pause
  \ytl{1920s}{Set theorists pursue additional axioms to
  settle~\textsc{ch} (one way or another).}
  \pause
  \ytl{1938}{Gödel proves: If~\textsc{zfc} is consistent, so
  is~\textsc{zfc}+\textsc{ch}.}
  \pause
  \ytl{1963}{Cohen proves: If~\textsc{zfc} is consistent, so
  is~\textsc{zfc}+$\neg$\textsc{ch}.}
  \pause
  \ytl{2011}{Hamkins offers his paper on the \hil{multiverse position} in
  the philosophy of set theory.}
  \pause
  %arguing that the program of pursuing
  %additional axioms (while successful in many ways) is doomed to fail
  %to settle~\textsc{ch}.}
  \ytl{2016}{Oldenziel proposes to study the modal multiverse of parametrized
  mathematics.}
  \parbox[b]{4.5em}{\hfill\phantom{x}}\makebox[0pt][c]{\phantom{b}}{\color{mypurple}\vrule}\\[-6.5pt]
  \parbox[b]{4.5em}{\hfill\phantom{x}}\makebox[0pt][c]{\phantom{b}}{\color{mypurple}\vrule}\\[-6.5pt]
  \parbox[b]{4.5em}{\hfill\phantom{x}}\makebox[0pt][c]{\phantom{b}}{\color{mypurple}\vrule}\\[-6.5pt]
\end{frame}
\begin{frame}{The set-theoretic multiverse}
  \begin{tikzpicture}[remember picture,overlay]
    \node[xshift=-1.5cm,yshift=-3.5cm] at (current page.north east)
    {\includegraphics[width=2cm]{branching}};
  \end{tikzpicture}
  \vspace*{-1.5em}
